\documentclass[a4paper,DIV=10]{scrartcl}


\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{float}


\newcommand{\op}[6]{
  \subsection{#1}
  #2
  
  \subsubsection*{Signature:}
  \ \ #3
  
  \subsubsection*{Context element (selectedEObject):}     
  \ \ #4
  
  \subsubsection*{Additional parameters:} 
  #5
  
  \subsubsection*{Precondition:}    
  \ \ #6
  
  \subsubsection*{Implementation in EMF Henshin:}
}

\newcommand{\cond}[3]{
	\subsection{#1}
	\label{subsec:#2}
	#3
}


\author{\textbf{Technical Report}\\
\hfill\\
Michaela Rindt, Timo Kehrer, Udo Kelter, Pit Pietsch\\
Software Engineering Group\\
University of Siegen}

\title{Rules for Edit Operations in Class Diagrams}

\date{rev. 2012-01-06}

% \title{
% A Catalog of Basic Edit Operations\\ for UML Class Models\\ \hfill \\
% \LARGE{Informal Specifications and Rule-based Implementations with EMF Henshin \hfill \\ \hfill \\}
% }

\begin{document}
\maketitle

\newpage
\tableofcontents

\newpage
\section{Introduction}

This technical report specifies edit operations for UML
class diagrams.
 We assume that the class diagrams are represented as
Ecore objects using the EMF technology.
 Each operation is specified as follows:

\begin{enumerate}
\item by a short informal description from a users' point
   of view

\item by a suggested signature of a method which
   implements this edit operation, and an informal
   description of the parameters in this signature

\item by the preconditions (informally specified) which must
   hold to successfully perform the edit operation

\item by an implementation of this edit operation as a
   Henshin transformation rule, which acts as a formal,
   precise specification.

\end{enumerate}

The main emphasis is on the formal specifications using
Henshin. These edit rules can be translated into software
which detects applications of these edit operations in 
a difference between two models, s. \cite{KeKT2011ASE}
for details.


\paragraph{Coverage of the UML Metamodel.} This catalog of
edit rules covers only the more important concepts of UML
class diagrams. For example, details such as
ValueSpecifications in multiplicities are not covered.
Future versions of this document will extend the set of
covered modelling concepts.

\paragraph{Used UML Metamodel.}
The creation of edit rules for class diagrams is based
on an internally developed UML Metamodel which is highly
truncated in comparison to the UML2.0 standard of the OMG \cite{OMG}.
This internal UML Metamodel is restricted to class diagrams only.
A concrete design difference lies e.g. in the construction of associations:
UML2.0 associations contain property elements which refer to the
target and source of the association. In the SiDiff UML Metamodel
an UMLAssociation contains so called UMLAssociationEnds wich refer
to the source and target of an association.
This is just one example of how these meta models differ.
If you are interested in how the SiDiff UML Metamodel is built,
please take a look at the according link under the references \cite{SiDiff-UML}.

\paragraph{Tooling.}
The edit operations were designed
with EMF-Henshin and EMF-Refactor.

EMF-Henshin provides a graphical user interface for
defining such edit operation, whereas EMF-Refactor is an
extension with which one can define preconditions to the
actual transformation process.

More Information about EMF-Henshin can be found under
their project page
\cite{Henshin}. To find more information about
EMF-Refactor visit the EMF-Refactor project page
\cite{Refactor}.



\subsection{Design Rules for Edit Operations} 

Some edit operations are obviously needed, e.g. operations
for creating and deleting model elements. This catalog
contains many additional operations, mostly ``move
operations'', which are not strictly necessary, but
convenient. An example of this is the operation which
moves a class into another package; instead of moving the
class, it could be deleted and reconstructed from scratch
in the other package.

Whenever possible, we have avoided to use undefined or default values. For
example, when creating a class, its name must be specified immediately in a parameter.

Another design decision was that each edit operation should be
implementable by one Henshin transformation.
 There are some model modifications which could be
implemented in different ways.

 Since the creation of Henshin transformations for UML is
still work in progress, this catalog of edit operations is
not yet complete and sometimes discretionary.




\subsection{Notations}

In general, every transformation consists of two files:
the (graphical) diagram file and the (more technical)
Henshin-graph file. In the latter, one can create
TransformationUnits which will define the execution
sequence of rules in different ways. In some cases of the
following transformations you will find excerpts of such
unit graphs for a better understanding.

Notations like 'nameValue/newName' show first the
parameter name used in the mainUnit of the graph-file and
secondly the placeholder name of the element in the
diagram-file.

Most conditions are very similar and are therefore just
listed once under the section 'Conditions'. You will find
a reference to these under relevant sections. 

Please note that the conditions are not yet complete.





\section{Conditions}
\input{Conditions}

\newpage
\section{Packages}
\input{Package}

\newpage
\section{Classes}
\input{Class}

\newpage
\section{Interfaces}
\input{Interface}

\newpage
\section{Enumerations}
\input{Enumeration}

\newpage
\section{Literals}
\input{Literal}

\newpage
\section{PrimitiveTypes}
\input{PrimitiveType}

\newpage
\section{Stereotypes}
\input{Stereotype}

\newpage
\section{Associations}
\input{Association}

\newpage
\section{AssociationClasses}
\input{AssociationClass}

\newpage
\section{AssociationEnds}
\input{AssociationEnd}

\newpage
\section{Generalizations}
\input{Generalization}

\newpage
\section{Operations}
\input{Operation}

\newpage
\section{Parameters}
\input{Parameter}

\newpage
\section{Attributes}
\input{Attribute}




%================== Bibliography ===============================================================
\newpage
\section{References}
\begin{thebibliography}{WW}

\bibitem {Henshin} \href{http://www.eclipse.org/modeling/emft/henshin/} {http://www.eclipse.org/modeling/emft/henshin/}.
 
\bibitem {Refactor} \href{http://www.eclipse.org/modeling/emft/refactor/} {http://www.eclipse.org/modeling/emft/refactor/}

\bibitem {SiDiff-UML} \href{http://pi.informatik.uni-siegen.de/qudimo/org.sidiff.uml/} {http://pi.informatik.uni-siegen.de/qudimo/org.sidiff.uml/}

\bibitem {OMG} \href{http://www.omg.org/} {http://www.omg.org/}

\bibitem {KeKT2011ASE} Kehrer, Timo; Kelter, Udo; Taentzer,
Gabriele: A Rule-Based Approach to the Semantic Lifting of
Model Differences in the Context of Model Versioning;
p.163-172 in: Proc. 26th IEEE/ACM International Conference
on Automated Software Engineering (ASE'11), 6-11 Nov 2011,
Lawrence, Kansas, USA; ACM; 2011

\end{thebibliography}






\end{document}

